Demanding resources: Agreement across characteristics seen as both challenges and resources

### 2022-10-11 SIOP2023/Counts/convergence.Rmd
caught a "hinderance"

The dissociation of challenges and hindrances may be important moving forward. @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers. However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions. We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking). The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator. @gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.

>>>>

The dissociation of challenges and hindrances may be important moving forward. @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers. However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking). The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator. @gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
